Clustering based on probability distributions with application on residential customers

### 2021-10-19 main.Rmd
validation intro section fixed

To validate the clustering approaches, we create data designs that replicate prototype behaviors that might be seen in electricity data contexts. We spiked several attributes in the data to see where one method works better than the other and where they might give us the same outcome or the effect of missing data <!---and trends--> on the proposed methods. A continuous measured variable $y$ of length $T$ indexed by $\{0, 1, \dots T-1\}$. Three circular granularities $g1$, $g2$ and $g3$ are considered with $2$, $3$ and $5$ levels respectively. Categories of $g1$, $g2$ and $g3$ are represented by ${g10,g11}$, ${g20, g21, g22}$ and ${g30, g31, g32, g33, g34}$. These categories could be integers or some more meaningful labels. For example, the granularity "day-of-week" could be either represented by ${0, 1, 2, \dots, 6}$ or ${Mon, Tue, \dots, Sun}$. We created independent replications $R = \{25, 250, 500\}$ of all data designs to see if our proposed clustering approaches can detect distinct designs in various groups for small, medium and large number of series. A sample size of $T=\{300, 1000, 5000\}$ is used in all designs to test small, medium and large sized series. The methods could preform differently with different jumps between consecutive categories. So a mean difference of $diff = \{1, 2, 5\}$ for corresponding categories are also considered. The code for creating these designs can be found in the Supplementary section (link to github repo). The results for $T=300$ and $R=25$ is shown, that means we have $25$ time series each with length $300$. The rest of the results could be found in the supplementary paper.

>>>>

To validate the clustering approaches, we create data designs that replicate prototype behaviors that might be seen in electricity data contexts. We spiked several attributes in the data to see where one method works better than the other and where they might give us the same outcome or the effect of missing data <!---and trends--> on the proposed methods. Three circular granularities $g1$, $g2$ and $g3$ are considered with categories denoted by ${g10,g11}$, ${g20, g21, g22}$ and ${g30, g31, g32, g33, g34}$ and levels $l_{g_1}=2$, $l_{g_2}=3$ and $l_{g_3}=5$. These categories could be integers or some more meaningful labels. For example, the granularity "day-of-week" could be either represented by ${0, 1, 2, \dots, 6}$ or ${Mon, Tue, \dots, Sun}$. Here categories of $g1$, $g2$ and $g3$ are represented by  $\{0, 1\}$, $\{0, 1, 2\}$ and $\{0, 1, 2, 3, 4\}$ respectively. A continuous measured variable $v$ of length $T$ indexed by $\{0, 1, \dots T-1\}$ is simulated such that it follows the structure across $g1$, $g2$ and $g3$. We created independent replications $R = \{25, 250, 500\}$ of all data designs to see if our proposed clustering approaches can detect distinct designs in various groups for small, medium and large number of series. A sample size of $T=\{300, 1000, 5000\}$ is used in all designs to test small, medium and large sized series. The methods could preform differently with different jumps between consecutive categories. So a mean difference of $diff = \{1, 2, 5\}$ for corresponding categories are also considered. The performance of the methods can vary with different number of significant granularities. So scenarios with all, few and just one significant granularities are considered. The code for creating these designs and the detailed results can be found in the Supplementary section (link to github repo).

<!-- The results for $T=300$ and $R=25$ is shown, that means we have $25$ time series each with length $300$. The rest of the results could be found in the supplementary paper. -->
